Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-25 RR_manuscript/Draft_RR.Rmd
:memo: edit reviewing process in RR draft

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
output:
  bookdown::pdf_document2:
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
geometry: margin=4cm
fontsize: 12pt
header-includes:
  - \usepackage{cleveref}
  - \setlength{\marginparwidth}{2cm}
  - \usepackage{changes}
  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
---

@@

<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN + TRANSITION -->

@@

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria: <!-- TR:Need flow chart here-->

"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:

- 100. A perfect analysis with no conceivable improvements from the reviewer.
- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
- 0. A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.

\*Please note that these values are meant to calibrate your ratings.
We welcome ratings of any number between 0 and 100."

After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:

\noindent "Please explain your ratings of this analysis.
\noindent Please evaluate the selection of acoustic features.
\noindent Please evaluate the measurement of acoustic features.
\noindent Please evaluate the choice of statistical analysis type.
\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
\noindent Please evaluate the suitability of the structure of the statistical model.
\noindent Please evaluate choices to exclude or not exclude subsets of the data.
\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice)."

After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings."

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
output:
  bookdown::pdf_document2:
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
geometry: margin=4cm
fontsize: 12pt
indent: true
header-includes:
  - \usepackage{cleveref}
  - \setlength{\marginparwidth}{2cm}
  - \usepackage{changes}
  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
---

@@

<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN + TRANSITION -->
To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g. *Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').

In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
The participant would read a sentence prompt out loud (*Du sollst den Würfel auf der <COLOR OBJECT> ablegen* 'You have to put the cube on top of the <COLOR OBJECT>') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der <COLOR OBJECT> ablegen* 'And now, you have to put the cube on top of the <COLOR OBJECT>') instructing the experimenter to move the cube on top of a different object (the *target*).

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (the Noun Focus condition, NF).
If the the objects were the same object but differed in color (e.g. *yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g. *Orangene Mandarine* 'orange mandarin'), medium typical (e.g. *Grüne Tomate* 'green tomato'), or atypical (e.g. *Gelbe Kirsche* 'yellow cherry').
The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.

@@

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:
<!-- TR:Need flow chart here-->

* Overall appropriateness of the acoustic analysis.
* Overall appropriateness of the statistical analysis.
* Choice of statistical analysis type.
* Model variables choice.
* Model specification.
* Data exclusion.
* Data transformation.

To help reviewers calibrate their rating, they will be given the following guidelines:

* 100. A perfect analysis with no conceivable improvements from the reviewer.
* 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
* 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
* 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
* 0. A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.

Furthermore, the reviewer will be given the option to include further comments in a text box.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
<!-- The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings." -->

### 2021-02-25 RR_manuscript/Draft_RR.tex
:memo: edit reviewing process in RR draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=4cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{cleveref}
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\hypertarget{the-data-set---the-prosody-of-redundant-modifiers}{%
\subsection{The data set - The prosody of redundant modifiers}\label{the-data-set---the-prosody-of-redundant-modifiers}}

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code, and the data set.
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria:

"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:

@@

*Please note that these values are meant to calibrate your ratings.
We welcome ratings of any number between 0 and 100."

After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:

\noindent ``Please explain your ratings of this analysis.
\noindent Please evaluate the selection of acoustic features.
\noindent Please evaluate the measurement of acoustic features.
\noindent Please evaluate the choice of statistical analysis type.
\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
\noindent Please evaluate the suitability of the structure of the statistical model.
\noindent Please evaluate choices to exclude or not exclude subsets of the data.
\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''

After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=4cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{cleveref}
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\hypertarget{the-data-set-the-acoustic-properties-of-redundant-modifiers}{%
\subsection{The data set: The acoustic properties of redundant modifiers}\label{the-data-set-the-acoustic-properties-of-redundant-modifiers}}

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.~the atypical \emph{a blue banana} vs the typical \emph{a yellow banana})?
More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon,' \emph{Rote Gurke} `red cucumber,' \emph{Rote Socken} `red socks').

In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der ablegen} `You have to put the cube on top of the ') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der ablegen} `And now, you have to put the cube on top of the ') instructing the experimenter to move the cube on top of a different object (the \emph{target}).

The two sentence prompts were used to create a focus contrast between the competitor and the target object.
If the competitor and target objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (the Noun Focus condition, NF).
If the the objects were the same object but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
The combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:

\begin{itemize}
\tightlist
\item
  Overall appropriateness of the acoustic analysis.
\item
  Overall appropriateness of the statistical analysis.
\item
  Choice of statistical analysis type.
\item
  Model variables choice.
\item
  Model specification.
\item
  Data exclusion.
\item
  Data transformation.
\end{itemize}

To help reviewers calibrate their rating, they will be given the following guidelines:

@@

Furthermore, the reviewer will be given the option to include further comments in a text box.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
